Estimating individual subjective values of emotion regulation strategies

### 2022-02-21 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
fixed typo
knitted document

library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","WorkspaceERED.RData"))

>>>>

library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown
library(BayesFactor) # for bayes factors

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","Workspace_ERED.RData"))
